Titulo

### 2014-12-18 RotacionOutFlows/Paper/ms.tex
New references in reference.bib file
cambios
fixes

\shortauthors{Remolina-Gutierrez, Forero-Romero \&Garavito-Camargo}

@@

Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
velocity at the sphere's surface. The minus/plus sign in the
$x$/$y$-component of the velocity indicates the direction of
rotation. In this case we take the angular velocity in the same
direction as the $\hat{k}$ unit vector.

In this work we use the analytical expression for rotation derived in [garavito-camargo et al]
where a rotating sphere can be seen as a static sphere in the laboratory
frame with a bulk velocity difference in each surface element with respect
to a distant observer. With the previous analysis the outcoming spectra can be
expressed as:

@@

---------------------------------------------------------------------\\
MISSING:\\
- Important equations and description of the parameters\\
- Why we use ThinShel instead of Wind. Its advantages (explains redshift, avoids re-difussion, bounces).\\
- Ref: Alvaro and Julian\\
-----------------------------------------------------------------------\\

@@

---------------------------------------------------------------------\\
MISSING IN REFERENCES: \\
- A loooot of references not here yet.\\
- Alvaro's paper.(Can galactic outflows explain the properties of Lyα emitters?
Alvaro Orsi, Cedric G. Lacey and Carlton M. Baugh)\\
- Use the correct citation method. \\
-----------------------------------------------------------------------\\

\bibliographystyle{apj}
\bibliography{references}

>>>>

\shortauthors{Remolina-Gutierrez, Forero-Romero \& Garavito-Camargo}

@@

Where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
velocity at the sphere's surface. The minus/plus sign in the
$x$/$y$-component of the velocity indicates the direction of
rotation. In this case we take the angular velocity in the same
direction as the $\hat{k}$ unit vector.\\

In this work we use the analytical expression for rotation derived in \citep{Garavito14} where a rotating sphere can be seen as a static sphere in the laboratory frame with a bulk velocity difference in each surface element with respect
to a distant observer. With the previous analysis the outcoming spectra can be
expressed as:

@@

\citep{Orsi12}

---------------------------------------------------------------------\\
MISSING:\\
- Important equations and description of the parameters\\
- Why we use ThinShell instead of Wind. Its advantages (explains redshift, avoids re-difussion, bounces).\\
-----------------------------------------------------------------------\\

@@

---------------------------------------------------------------------\\
MISSING IN REFERENCES: \\
- Alvaro's paper.(Can galactic outflows explain the properties of Lyα emitters?
Alvaro Orsi, Cedric G. Lacey and Carlton M. Baugh)\\
- Use the correct citation method. \\
-----------------------------------------------------------------------\\

\bibliographystyle{latex/apj}
\bibliography{references}
